PS753 Glossary

### 2022-02-01 _academics/ps753-glossary/ps753-glossary.Rmd
build
update citation

xxx see https://corescholar.libraries.wright.edu/cgi/viewcontent.cgi?article=2427&context=knoesis

@@

>>>>

(See @alhazmiUnderstandingSocialEffects2015)

@@

![homer](homer.png)
In the example above, there are 8 nodes that Homer (center) could connect to; among those 8 nodes, there are 7 + 6 + 5 + 4 + 3 + 2 + 1 = 28 possible undirected connections (not connecting to Homer), and 9 of those 28 do exist, for a local clustering coefficient of 9/28 = 0.32.
